\Title

### 2021-05-10 latex/paper/main.tex
Wrote the rest of the simulation section, v1

The level set \(E_\pi\) with energy \(E(\pi,0)\) is outlined in black. 
Due to the model mismatch, \(E_\pi\) is no longer the boundary between
rotations and oscillations.
The oscillation domain is actually much larger: orbits rotate once they hit the
\(p_u\)-axis at \(\abs{p_u} \approx 0.15\), while \(E_\pi\) intersects the
\(p_u\)-axis at \(\abs{p_u} \approx 0.055\).
Despite this, the VNHC still injects energy into the acrobot.
The points where the orbit exits \(E_\pi\) are marked with black stars,
with the final departure marked by a red star.
After this final departure, the acrobot begins rotating and continues to gain
energy over time.

@@

To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo simulation \cite{montecarlo} where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured the how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 10--35 seconds.

@@

According to Theorem \ref{thm:acrobot-energy-stabilization}, a negative value
of \(I\) should dissipate energy from the acrobot.
To test this, we initialized our acrobot with a rotation at the phase
\((q_u,p_u) = (0,0.18)\),  set \(I = -10\), and simulated the constrained
dynamics for \(30\) seconds.
The resulting orbit is plotted in Figure \ref{fig:acrobot-diss-orbit}. 
As is expected, the acrobot slows down over time.
We again highlight the locations where the orbit crossed the set \(E_\pi\) in
black, with the final crossing in red. 
After this crossing, the acrobot ceased rotating and its oscillations decayed to
zero.

@@

\subsection{Energy Regulation}

To test how VNHCs can perform energy regulation, we employed a simple supervisor
which toggles between injection and dissipation VNHCs to stabilize an
orbit which crosses the \(q_u\)-axis at some desired angle (for oscillations) or
the \(p_u\)-axis at some desired velocity (for rotations).
Specifically, one chooses some appropriate energy value \(E_0 > 0\) and a hysteresis
percentage \(\delta \in [0,1]\).
The supervisor enables the injection VNHC if 
\(E(q_u,p_u) < (1-\delta)E_0\), the dissipation VNHC if 
\(E(q_u,p_u) > (1+\delta) E_0\), and it keeps the leg angle constant if
\((1-\delta)E_0 \leq E(q_u,p_u) (1+\delta)\leq E_0\).

First, we wanted the acrobot to oscillate with a maximum body angle 
\(q_u = \pi/2\).
The corresponding energy is \(E_0 = E(\pi/2,0)\), and we set our hysteresis to
be \(\delta = 5\%\).
\textbf{TODO: do the energy regulation experiment and see the results.}

\subsection{Summary of Results}
The simulation results in this section demonstrate the energy regulation
capabilities of our VNHC.  
In particular, Theorem \ref{thm:acrobot-energy-stabilization} appears to work
even for acrobots whose limbs have differing masses and lengths.
The energy regulation supervisor does not

>>>>

The level set \(E_\pi\) with energy \(E(\pi,0)\) is outlined in black.
Despite the change in acrobot model, this level set remains the boundary
between oscillations and rotations for the nominal pendulum.
The points where the orbit exits \(E_\pi\) are marked with black stars,
with the final departure marked by a red star.
Interestingly, our choice of \(I\) is large enough that we observe significant
differences between the nominal pendulum and the constrained dynamics:
\(E_\pi\) intersects the \(p_u\)-axis at \(\abs{p_u} \approx 0.18\), yet the
constrained acrobot begins rotating once it hits the
\(p_u\)-axis at \(\abs{p_u} \approx 0.16\). 
This indicates that higher values of \(I\) enable the acrobot to gain energy
faster and begin rotating sooner, so long as the actuator does not saturate.

@@

To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo simulation \cite{montecarlo} where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 10--35 seconds.

@@

According to Theorem \ref{thm:acrobot-energy-stabilization}, a negative value
of \(I\) will dissipate energy from the acrobot.
To test this, we initialized our acrobot with a rotation at the phase
\((q_u,p_u) = (0,0.18)\),  set \(I = -10\), and simulated the constrained
dynamics for \(30\) seconds.
The resulting orbit is plotted in Figure \ref{fig:acrobot-diss-orbit}. 
As expected, the acrobot slows down over time.
We again highlight the locations where the orbit crossed the set \(E_\pi\) in
black, with the final crossing in red. 
After this crossing, the acrobot ceased rotating and its oscillations decayed to
zero.

@@

\subsection{Oscillation Regulation}

Once can use a simple supervisor to stabilize oscillations by appropriately
toggling between injection and dissipation VNHCs.
Specifically, one chooses a desired oscillation angle 
\(q_\text{des} \in \, ]0,\pi[\) and, to avoid infinite switching, a
hysteresis value \(\delta \in [0,1]\) 
Each time the orbit crosses the \(q_u\)-axis (i.e. \(p_u = 0\)) or 
when \(|q_u| = \pi\), the supervisor changes which VNHC is enforced as follows:
\begin{itemize}
    \item If \(|q_u| < (1-\delta)q_\text{des}\), enable the injection VNHC.
    \item If \(|q_u| > (1+\delta)q_\text{des}\), enable the dissipation VNHC.
    \item If \((1-\delta)q_\text{des} \leq |q_u| \leq (1+\delta)q_\text{des}\),
        keep the leg extended at \(q_a = 0\). This can be done continously since
        \(q_a = 0\) when \(p_u = 0\).
\end{itemize}

Figure \ref{fig:acrobot-osc-reg} shows the supervisor stabilizing an
oscillation with body angle \(q_\text{des} = \pi/2\) and a 
\(5\%\) hysteresis, meaning \(\delta = 0.05\).
The supervisor reevaluated its choice of VNHC at each black star;  
the red circle corresponds to the part of the orbit where the supervisor kept
the leg extended, because the oscillation was within tolerance of
\(q_\text{des}\).

In Figure \ref{fig:acrobot-osc-reg-in} the acrobot was initialized at 
\((q_u,p_u) = (\pi/32,0)\); here the supervisor injected energy for most of the
orbit.
In Figure \ref{fig:acrobot-osc-reg-diss} the acrobot was initialized at the rotation
\((q_u,p_u) = (0,0.19)\); here the supervisor dissipated energy. 
In both cases, the supervisor stabilized the desired oscillation .

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_osc_orbit_1.png}
        \caption{Stabilizing an oscillation from below.}
        \label{fig:acrobot-osc-reg-in}
    \end{subfigure}
    \begin{subfigure}[t]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_osc_orbit_2.png}
        \caption{Stabilizing an oscillation from above.}
        \label{fig:acrobot-osc-reg-diss}
    \end{subfigure}
    \caption{Using a supervisor to stabilize the oscillation with peak angle
    \(q_\text{des} = \pi/2\).}
    \label{fig:acrobot-osc-reg}
\end{figure}

\subsection{Rotation Regulation}
Along with stabilizing oscillations, one can use a supervisor to stabilize
rotations.
In this case, one chooses a desired rotation rate \(p_\text{des} > 0\) and a
hystersis value \(\delta \in [0,1]\).
Each time the orbit crosses the \(p_u\)-axis (i.e. when \(q_u = 0\)), the
supervisor changes which VNHC is enforced as follows:
\begin{itemize}
    \item If \(|p_u| < (1-\delta)p_\text{des}\), enable the injection VNHC.
    \item If \(|p_u| > (1+\delta)p_\text{des}\), enable the dissipation VNHC.
    \item If \((1-\delta)p_\text{des} \leq |p_u| \leq (1+\delta)p_\text{des}\),
        extend the leg fully by setting \(q_a = 0\).
        For these simulations, we assume this can be done instantaneously.
\end{itemize}

Rotation regulation is demonstrated in Figure \ref{fig:acrobot-rot-reg}, where
the supervisor stabilizes \(p_\text{des} = 0.19\) with a \(2\%\) hysteresis 
\(\delta = 0.02\).
The supervisor changed its choice of VNHC at each black star until it finally extended
the leg (shown in red).

In Figure \ref{fig:acrobot-rot-reg-in} the acrobot was initialized at the
oscillation \((q_u,p_u) = (\pi/2,0)\); here the supervisor injected energy until
the orbit hit the \(p_u\)-axis near \(p_\text{des}\).
In Figure \ref{fig:acrobot-rot-reg-diss} the acrobot was initialized at the
faster rotation \((q_u,p_u) = (0, 0.23)\); the supervisor dissipated energy.
In both cases, the desired rotation was stabilized correctly.

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_rot_orbit_1.png}
        \caption{Stabilizing a rotation from below.}
        \label{fig:acrobot-rot-reg-in}
    \end{subfigure}
    \begin{subfigure}[t]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_rot_orbit_2.png}
        \caption{Stabilizing a rotation from above.}
        \label{fig:acrobot-rot-reg-diss}
    \end{subfigure}
    \caption{Using a supervisor to stabilize the rotation with maximal momentum
    \(p_\text{des} = 0.23\).}
    \label{fig:acrobot-rot-reg}
\end{figure}

\subsection{Summary of Results}
The simulation results in this section demonstrate the energy regulation
capabilities of our VNHC.  
We were able to stabilize both oscillations and rotations by implementing a
control supervisor which toggled between injection, dissipation, and
leg-extension VNHCs.
In particular, these simulations indicate that our VNHC
works even for acrobots whose limbs have differing masses and lengths.
